Miscellaneous notes for D. Huybrechts's Complex Geometry

### 2016-09-20 Complex Geometry - index/misc/complex geometry-misc.tex
Finished one problem of complex geometry! Oh yeah.

        However, I still have doubts about the following question:
        For $A\in \mathrm{GL}(2n,\mathbb{R})$, if $AJA^{-1}=J$, can we
        conlude that $A$ is inside $\mathrm{GL}(n,\mathbb{C})$?
        % TODO resolve this double.
        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}
            }

>>>>

        However, I still have doubts about the following question:
        For $A\in \mathrm{GL}(2n,\mathbb{R})$, if $AJA^{-1}=J$, can we
        conlude that $A$ is inside $\mathrm{GL}(n,\mathbb{C})$?

        The following is my solution:
        \begin{lemma}
            There exists a injection $\phi$ of $\mathrm{GL}(n,\mathbb{C})
            \hookrightarrow \mathrm{GL}(2n,\mathbb{R})$ such that:
            \begin{align}
                \phi(i B)= \phi(i)\phi(B)
            \end{align}
            for any $B\in \mathrm{GL}(n,\mathbb{C})$. Also, for any
            $A\in \mathrm{GL}(2n,\mathbb{R})$ we have $AJA^{-1}=J$
            if and only if $A\in \mathrm{Im}(\phi)$, where $J\equiv\phi(i)$.
        \end{lemma}

        \begin{proof}
            The $\phi$ is construct as follows. Let 
            $J_0=\left( \begin{array}{cc}
                 0 & -1 \\
            1 & 0 \\ \end{array} \right)$, define $H(x+iy)$ for
            $x,y\in \mathbb{R}$ as
            \begin{align}
                H(x+iy) = x I + y J
            \end{align}
            Then:
            \begin{align}
                \phi(A)_{ij} \equiv H(a_{ij})
            \end{align}
            Then:
            \begin{align}
                \phi(i) = \left( \begin{array}{ccc}
                     J & 0 & 0 \\
                     0 & \text{...} & 0 \\
                     0 & 0 & J \\
                    \end{array} \right)
            \end{align}
            By direct simple calculation (remember to use the technique
            of block multiplication), we have:
            $\phi(i B)= \phi(i)\phi(B)$.
            for any $B\in \mathrm{GL}(n,\mathbb{C}$. This shows also
            $BJB^{-1}=J$, since $iB=Bi$.

            To prove the converse, we see that the following matrices forms
            a basis of $2x2$ real matrices:
            $$ \left( \begin{array}{cc}
             1 & 0 \\
             0 & 1 \\ \end{array}
            \right),\left( \begin{array}{cc}
             0 & -1 \\
             1 & 0 \\ \end{array}
            \right),\left( \begin{array}{cc}
             0 & 0 \\
             1 & 0 \\ \end{array}
            \right),\left( \begin{array}{cc}
             0 & 0 \\
             0 & 1 \\ \end{array} \right) $$
            They are denoted, from left to right as $I,J_0,K,L$.
            \marginpar{Fun fact: $[K,J_0]=\sigma_z\;,[L,J_0]=\sigma_x$, the
            pauli matrices!}
            Let any $A\in \mathrm{GL}(2n,\mathbb{R})$, we can partition $A$
            into a matrix of $2x2$ matrices $(a_{ij})$. Each matrix can
            the be expressed as $a_{ij}=x_{ij}I+y_{ij}J_0+z_{ij}K+t_{ij}L$.
            Then if $AJA^{-1}=J$, by direct calculation we find:
            $$ (z_{ij}K+t_{ij}L)J_0=J_0(z_{ij}K+t_{ij}L)$$
            then also by direct calculation, it can be easily found that
            $z_{ij}=t_{ij}=0$. Hence $A\in \mathrm{Im}(\phi)$.
        \end{proof}

        \subsubsection{Why \texorpdfstring{
                $GL(n, \mathbb{C}) \hookrightarrow GL^+(2n,\mathbb{R})$
                }{}
            }
